Verifying Demonstrations

### 2019-09-09 paper/DB-anon-cred.tex
Improves typesetting for MF resistance proof

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = (q+k)^n (kq)^{-n}\), where \(k, q\) are as 
  in \cref{DB-Schnorr}.
\end{theorem}

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields a success with probability 
    \(\frac{1}{k}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}
  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
  thus \[\left(\frac{1}{k}+\frac{1}{q}\right)^n = (q + k)^n (kq)^{-n}\] in 
  total per protocol session.
\end{proof}

>>>>

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{k}+\frac{1}{q}\right)^n\), 
  where \(k, q\) are as in \cref{DB-Schnorr}.
\end{theorem}

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields a success with probability 
    \(\frac{1}{k}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}
  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
  thus \(\left(\frac{1}{k}+\frac{1}{q}\right)^n\) in total per protocol 
  session.
\end{proof}
